\chapter{Results}
\lhead{\emph{Results}}

\section{Scientific results}
This section will contain data, visualizations and results from our work towards our scientific problem. 

\section{Engineering results}
This section will contain how our example project/proof of concept has turned out in terms of goals set in earlier stages of the project. Since our project is not a traditional software engineering bachelors project we will try to evaluate our project based on the goals set in some of the meetings with the product owners. % Resultat fra tester skal være lagt her
%
The engineering goal in this project was to firstly create a proof of concept application which can display it's usefulness. Although the project owners did not set an lower bound for accuracy they insinuated that the application/module should be a resource for Matistikk. In the true spirit of an agile mindset the product was evaluated with our product owners continuously, to discuss improvements and changes. This also led to a stage in which the proof of concept application worked, looked and performed to be a resource for Matistikk. After becoming quite satisfied with how the application worked, blablabla....... bla bla bla
% ER DETTE FOR LIKT METODE ??

% 

% 
\section{Administrative results}
This section will contain results from an administrative perspective. This includes the planning, implementation and achievements of project goals.
\quad
The nature of this assignment led the project first into a software development phase, closely followed by a research phase. Both phases was highly influenced by an agile mindset, although the software development phase was actually planned with sprints and reviews. Attempts were made on planning the research phase, but much of the time went into knowing artificial neural networks. \\
In the software development phase an agile mindset was always in the background, every critical decision and choice was discussed, this was an important aspect of the teamwork. The project required us to deliver fast and learn from our experiences to improve. If one of the project engineers did not understand or was not present when choices were made, it could lead to confusion and loss of progression. It made stand-up meetings, or a quick status meeting quite important.

% FIGUR AGIL ITERATIV


% FIGUR RESEARCH ITERATIV


% TABELL OPPMØTE ??? trengs det??

% TRENGS DETTE?
Throughout the project, Thursdays became a work day, because of part-time jobs and a course that was finished mid march.

% NØDVENDIG?
% BRUK AV TRELLO TABELL